Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-17 paper/manuscript.tex
Fixes in perturbation map section

    \caption{\textbf{Examples of perturbation networks} A: Star shaped network with the crystal structure in the center. B: Network with cycle closures. Arrows indicate the direction of the perturbation. Green cycles indicate good cycle closure, red poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystal structure binding mode.}

@@

In some cases, during the lead optimization stage, or if perturbations would be rather large a star shaped network as seen in Fig.~\ref{fig:fig_types_of_networks} (A) is used.. However, adding redundancy into the network means that a better error analysis can be carried out, by looking at cycle closure errors as discussed in sec.~\ref{subsec:predictions}, with an example given in Fig.~\ref{fig:fig_types_of_networks}.

@@

\paragraph{Constraints and relative free energy calculations.}

@@

Commonly, bonds involving hydrogen are constrained to a fixed length using algorithms such as SHAKE or LINCS, allowing the use of longer timesteps~\cite{}.

@@

At present the most general solution to this problem is simply to avoid the use of constraints (and thus use a smaller timestep if necessary, usually of around 1 fs) in any relative free energy calculation involving a transformation of a constrained bond.

@@

    \caption{\textbf{Absolute thermodynamic cycle}}

>>>>

    \caption{\textbf{Examples of perturbation networks} \textbf{A} Star shaped network with the crystal structure in the center. \textbf{B} Network with cycle closures (see more on this in Sec.~\ref{sec:are-they-good}). Arrows indicate the direction of the perturbation. Green cycles indicate good cycle closure, red poor cycle closure. The red arrow indicates a poorly converged simulation that would give rise to bad cycle closures. The diamond indicates the use of a crystal structure binding mode.}

@@

In some cases, during the lead optimization stage, or if perturbations would be rather large a star shaped network as seen in Fig.~\ref{fig:fig_types_of_networks} (\textbf{A}) is used. However, adding redundancy into the network means that a better error analysis can be carried out, by looking at cycle closure errors as discussed in sec.~\ref{sec:are-they-good}, with an example given in Fig.~\ref{fig:fig_types_of_networks} (\textbf{B}).

@@

\paragraph{Constraints and relative free energy calculations}

@@

Commonly, bonds involving hydrogen are constrained to a fixed length using algorithms such as SHAKE or LINCS, allowing the use of longer timesteps~\cite{krautler2001fast}.

@@

At present the most general solution to this problem is simply to avoid the use of constraints (and thus use a smaller timestep if necessary, usually of around 1 fs) in any relative free energy calculation involving a transformation of a constrained bond, as done by GROMACS. 

@@

    \caption{\textbf{Thermodynamic cycle required for an aboslute free energy calculation}}
